\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-26 OaklandSubmission/ld.tex
till compilation rules

@@

\TODO{Do we want to write things in logical order or order in paper?}

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Base type} & \sigma &::=& \kw{uint} \mid \kw{bool}\\
    \ftext{Type} & \psi &::=& \sigma \mid \sigma[n]\\
    \ftext{Constant} & c &::=& n \mid \top \mid \bot\\
    \ftext{Expression} & e &::=& c \mid x \mid e_{1} + e_{2} \mid e_{1} > e_{2} \mid \cond{e_{1}}{e_{2}}{e_{3}}\\
    & &\mid& [\overline{e_{i}}]_{n} \mid x[e] \mid \kw{in}_{j}\\
    \ftext{Statement} & s &::=& \psi\:x = e \mid x := e \mid \for{x}{n_{1}}{n_{2}}{s}\\
    & & \mid& x[e_{1}] := e_{2} \mid \ite{e}{s_{1}}{s_{2}} \mid \kw{out}\:e \mid s_{1}; s_{2}\\
    & & \mid& \loops{x}{n}{s}
  \end{array}
  \]
\caption{Source language}
\label{fig:srclang}
\end{figure}

@@

    \inferrule*[lab={\footnotesize{E-Add}}]
               {
                 \forall i \in \{1, 2\}.\:\rho \vdash e_{i} \Downarrow n_{i}
               }
               {
                 \rho \vdash e_{1} + e_{2} \Downarrow n_{1} + n_{2}
               }

@@

\subsubsection*{Source language}Our source language
(\figureref{srclang}) is a simple imperative language. Types
$\psi$ consist of the base types $\sigma$, and arrays
of base types $\sigma[n]$, where $n$ is the array length. Though we
model only one dimensional arrays, our implementation supports higher
dimensional arrays as well. Expressions $e$ in the language include the
integer constants $n$, \kw{bool} constants $\top$ and $\bot$,
variables $x$, binary operations $e_{1} + e_{2}$ and $e_{1} > e_{2}$,
conditionals $\cond{e}{e_{1}}{e_{2}}$, array literals 
$[\overline{e_{i}}]_{n}$\footnote{We write $\overline{e}$ (and
  similarly for other symbols) to denote a sequence of expressions.
The length of the sequence is usually clear from the context.}, and
array reads $x[e]$. The expression $\kw{in}_{j}$ denotes input from
party $j$. The statements $s$ in the language comprise of variable
declarations and assignments ($\psi\:x = e$ and $x := e$ resp.),
\kw{for} loops, array writes ($x[e_{1}] := e_{2}$), \kw{if}
statements, and sequence of statements ($s_{1}; s_{2}$). The statement
$\kw{out}\:e$ denotes revealing the value of $e$ to the
parties. The \kw{while} statement is an internal syntax that is not
exposed to the programmer.

@@

The judgment $\rho \vdash e \Downarrow v$ denotes the big-step
evaluation of an expression~$e$ to a value~$v$ under the runtime
environment~$\rho$. Rule ({\sc{E-Var}}) looks up the value of $x$ in
the environment. Rule ({\sc{E-Add}}) inductively evaluates $e_{1}$ and
$e_{2}$, and evaluates to their sum. Rule ({\sc{E-Read}})
evaluates an array read operation. It first evaluates $x$ to an array
value $[\overline{c_{i}}]_{n_{1}}$, and $e$ to a \kw{uint} value
$n$. It then returns $c_{n}$, the $n$-th index value in the array,
provided $n < n_{1}$, the length of the array. Rule ({\sc{E-Inp}})
evaluates to some constant $c$ denoting party $j$'s input. We model
the inputs to be base constants, an array input can be written in the
language as $[\kw{in}_{j}]_{n}$, which can then evaluate using the
rule ({\sc{E-Arr}}). The remaining rules are straightforward, and are
elided for space reasons.

@@

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Secret label} & m &::=& \mathcal{A} \mid \mathcal{B}\\
    \ftext{Label} & \ell &::=& \mathcal{P} \mid m\\
    \ftext{Type} & \tau &::=& \sigma^{\ell} \mid \sigma^{\ell}[n]\\
    \ftext{Expression} & \widetilde{e} &::=& c \mid x \mid \widetilde{e_{1}} +_{\ell} \widetilde{e_{2}} \mid \widetilde{e_{1}} >_{\ell} \widetilde{e_{2}} \\
    & & \mid & \lcond{\ell}{{\widetilde{e}}}{{\widetilde{e_{1}}}}{{\widetilde{e_{2}}}} \mid x[\widetilde{e}] \mid [\overline{\widetilde{e_{i}}}]_{n} \mid \kw{in}^{m}_{j} \mid \widetilde{e} \rhd m\\
    \ftext{Statement} & \widetilde{s} &::=& \tau\:x = \widetilde{e} \mid x := \widetilde{e} \mid \dots \mid \widetilde{s_{1}}; \widetilde{s_{2}} \mid \dots\\
  \end{array}
  \]
\caption{Intermediate Language}
\label{fig:interlang}
\end{figure}

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{add}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \bval \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Is environ misplaced?}}
\label{fig:circuits}
\end{figure}

@@

Most of the expression forms $\widetilde{e}$ are same as $e$, except
that the binary operators, and the conditional forms
are annotated with label $\ell$, denoting how the operators should be
evaluated ($\mathcal{P}$ for in-clear, and $\mathcal{A}$ and
$\mathcal{B}$ for using arithmetic or boolean circuits resp.). The
form $\widetilde{e} \rhd m$ denotes coercing \divya{the value of} $\widetilde{e}$ to be
$m$-secret shared. The statements $\widetilde{s}$ are analogous to
$s$.

@@

@@

\begin{figure}
  \small
  \fbox{$\Gamma \vdash e : \tau \leadsto \widetilde{e}$}
  \[
  \begin{array}{c}
     \inferrule*[lab={\footnotesize{T-Cons}}]
               {
                 \tau = \mathsf{typeof}(c)^{\mathcal{P}}
               }
               {
                 \Gamma \vdash c : \tau \leadsto c 
               }

     \inferrule*[lab={\footnotesize{T-Add}}]
               {
                 \forall i \in \{1,2\}.\:\Gamma \vdash e_{i} : \kw{uint}^{\ell} \leadsto \widetilde{e_{i}}\\\\
                 \ell = \mathcal{P} \vee \ell = \mathcal{A}
               }
               {
                 \Gamma \vdash e_{1} + e_{2} : \kw{uint}^{\ell} \leadsto \widetilde{e_{1}} +_{\ell} \widetilde{e_{2}}
               }

    %%  \inferrule*[lab={\footnotesize{T-Var}}]
    %%            {
    %%            }
    %%            {
    %%              \Gamma \vdash x : \Gamma(x) \leadsto x
    %%            }
\\\\
     \inferrule*[lab={\footnotesize{T-Gt}}]
               {
                 \forall i \in \{1,2\}.\:\Gamma \vdash e_{i} : \kw{uint}^{\ell} \leadsto \widetilde{e_{i}}\\\\
                 \ell = \mathcal{P} \vee \ell = \mathcal{B}
               }
               {
                 \Gamma \vdash e_{1} > e_{2} : \kw{bool}^{\ell} \leadsto \widetilde{e_{1}} >_{\ell} \widetilde{e_{2}}
               }

     \inferrule*[lab={\footnotesize{T-Cond}}]
               {
                 \Gamma \vdash e : \kw{bool}^{\ell} \leadsto \widetilde{e}\\\\
                 \forall i \in \{1,2\}.\:\Gamma \vdash e_{i} : \sigma^{\ell_{1}} \leadsto \widetilde{e_{i}}\\\\
                 \ell = \mathcal{P} \vee (\ell = \mathcal{B} \wedge \ell' =\mathcal{B})
               }
               {
                 \Gamma \vdash \cond{e}{e_{1}}{e_{2}} : \sigma^{\ell_{1}} \leadsto \lcond{\ell}{\widetilde{e}}{\widetilde{e_{1}}}{\widetilde{e_{2}}}
               }

     \inferrule*[lab={\footnotesize{T-Arr}}]
               {
                 \forall i \in \{0 \dots n - 1\}.\:\Gamma \vdash e_{i} : \sigma^{\ell} \leadsto \widetilde{e_{i}}
               }
               {
                 \Gamma \vdash [\overline{e_{i}}]_{n} : \sigma^{\ell}[n] \leadsto [\overline{\widetilde{e_{i}}}]_{n}
               }

  \end{array}
  \]
  \\\\
    \fbox{$\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$}
  \[
  \\
  \begin{array}{c}
     \inferrule*[lab={\footnotesize{T-Decl}}]
               {
                 \psi = \sigma \Rightarrow \tau = \sigma^{\ell}\\\\
                 \psi = \sigma[n] \Rightarrow \tau = \sigma^{\ell}[n]\\\\
                 \Gamma \vdash e : \tau \leadsto \widetilde{e}
               }
               {
                 \Gamma \vdash \psi\:x = e \leadsto \tau\:x = \widetilde{e} \mid \Gamma, x:\tau
               }

\subsubsection*{Compilation judgments} We now come to the compilation
rules shown in Figure~\ref{fig:compile}. We present the rules in a
declarative style, where the rules are non-syntax
directed, and the labels $\ell$ are chosen
non-deterministically. Section~\ref{sec:impl} describes the inference
scheme in our implementation.

Judgment $\Gamma \vdash e : \tau \leadsto \widetilde{e}$, where
$\Gamma$ maps variables $x$ to types $\tau$, says that
under $\Gamma$, $e$ compiles to $\widetilde{e}$ with type $\tau$.

The rule ({\sc{T-Cons}}) assigns the label $\mathcal{P}$ to the
constants, as the constants are always public. Rule ({\sc{T-Add}})
compiles an addition to either public addition ($+_{\mathcal{P}}$), or
secret addition using an arithmetic circuit ($+_{\mathcal{A}}$). As
our compiler is cryptographic cost aware, it never compiles the
addition to boolean addition $+_{\mathcal{B}}$. In a similar manner,
rule ({\sc{T-Gt}}) compiles $e_{1} > e_{2}$ to either public comparison,
or secret comparison using boolean circuits. The rule for conditional
({\sc{T-Cond}}) has two cases: when the conditional expression $e$ is of
type $\kw{bool}^{\mathcal{P}}$, both the branches have a base type
$\sigma^{\ell_{1}}$, for an arbitrary $\ell_{1}$, and the conditional is
compiled to public conditional, whereas when the conditional
expression has type $\kw{bool}^{\mathcal{B}}$, $\ell_{1}$ is also
$\mathcal{B}$, and the conditional is compiled to a secret conditional
using a boolean circuit. Note that we restrict the type of the branches
to be of base type. Rule ({\sc{T-Read}}) types an array read. It checks
that the array index $e$ is public, and uses a static bounds checking
judgment $\Gamma \models e < n$ to prove that the array index is in
bounds. Section~\ref{sec:impl} discusses our implementation of bounds
checking. Rule ({\sc{T-Inp}}) picks a label $m$ for the input. Finally,
rule ({\sc{T-Sub}}) is the subsumption rule that coerces an expression of
type $\sigma^{\ell}$ to an expression of type $\sigma^{m}$ using the
coerce expression. Importantly, secrets cannot be coerced to public
values.

Judgment $\Gamma \vdash s : \tau \leadsto \widetilde{s} \mid \Gamma_{1}$
compiles a statement $s$ resulting in the statement $\widetilde{s}$
and type environment $\Gamma_{1}$. Rule ({\sc{T-Decl}}) picks a label
$\ell$, and adds the binding for $x$ to the environment. Rule
({\sc{T-For}}) adds the loop counter $x$ to $\Gamma$ at type
$\kw{uint}^{\mathcal{P}}$, and delegates type checking to the
\kw{while} form. The rule ({\sc{T-Write}}), similar to ({\sc{T-Read}}),
checks that the index has type $\kw{uint}^{\mathcal{P}}$, and is in
bounds. Rule ({\sc{T-Out}})
types the expression $e$ at some secret label $m$. Rule ({\sc{T-If}})
checks that the conditional expression is public, and rule
({\sc{T-Seq}}) sequences the type environments. Finally, the typing
rule for the (internal) \kw{while} form ensures that $x$ is mapped in
$\Gamma$ at type $\kw{uint}^{\mathcal{P}}$, and that $x \notin
\mathsf{modifies}(s)$--this is necessary for ensuring the termination
of our semantics.

>>>>

\TODO{Use mult op instead of add? arguments of using arithmetic are clearer there; though we also use arithmetic always for add also. Or write both in exp and write rule for mul; how about bit-wise And? shifts?
Say that more exp written in implementation}

@@

%\TODO{Do we want to write things in logical order or order in paper?}

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Base type} & \sigma &::=& \kw{uint} \mid \kw{bool}\\
    \ftext{Type} & \psi &::=& \sigma \mid \sigma[n]\\
    \ftext{Constant} & c &::=& n \mid \top \mid \bot\\
    \ftext{Expression} & e &::=& c \mid x \mid e_{1} \mulop e_{2} \mid e_{1} > e_{2} \mid \cond{e_{1}}{e_{2}}{e_{3}}\\
    & &\mid& [\overline{e_{i}}]_{n} \mid x[e] \mid \kw{in}_{j}\\
    \ftext{Statement} & s &::=& \psi\:x = e \mid x := e \mid \for{x}{n_{1}}{n_{2}}{s}\\
    & & \mid& x[e_{1}] := e_{2} \mid \ite{e}{s_{1}}{s_{2}} \mid \kw{out}\:e \mid s_{1}; s_{2}\\
    & & \mid& \loops{x}{n}{s}
  \end{array}
  \]
\caption{Source language}
\label{fig:srclang}
\end{figure}

@@

    \inferrule*[lab={\footnotesize{E-Mult}}]
               {
                 \forall i \in \{1, 2\}.\:\rho \vdash e_{i} \Downarrow n_{i}
               }
               {
                 \rho \vdash e_{1} \mulop e_{2} \Downarrow n_{1} \mulop n_{2}
               }

@@

\subsubsection*{Source language} Our source language
 is a simple imperative language. \divya{We present the core of our language in \figureref{srclang} but our implementation is more expressive (see \sectionref{impl}).} Types
$\psi$ consist of the base types $\sigma$, and arrays
of base types $\sigma[n]$, where $n$ is the array length. Though we
model only one dimensional arrays, our implementation supports higher
dimensional arrays as well. Expressions $e$ in the language include the
integer constants $n$, \kw{bool} constants $\top$ and $\bot$,
variables $x$, binary operations $e_{1} \mulop e_{2}$ and $e_{1} > e_{2}$,
conditionals $\cond{e}{e_{1}}{e_{2}}$, array literals 
$[\overline{e_{i}}]_{n}$\footnote{We write $\overline{e}$ (and
  similarly for other symbols) to denote a sequence of expressions.
The length of the sequence is usually clear from the context.}, and
array reads $x[e]$. The expression $\kw{in}_{j}$ denotes input from
party $j$. The statements $s$ in the language comprise of variable
declarations and assignments ($\psi\:x = e$ and $x := e$ resp.),
\kw{for} loops, array writes ($x[e_{1}] := e_{2}$), \kw{if}
statements, and sequence of statements ($s_{1}; s_{2}$). The statement
$\kw{out}\:e$ denotes revealing the value of $e$ to the
parties. The \kw{while} statement is an internal syntax that is not
exposed to the programmer. \\

@@

The judgment $\rho \vdash e \Downarrow v$ denotes the big-step
evaluation of an expression~$e$ to a value~$v$ under the runtime
environment~$\rho$. Rule ({\sc{E-Var}}) looks up the value of $x$ in
the environment. Rule ({\sc{E-Mult}}) inductively evaluates $e_{1}$ and
$e_{2}$, and evaluates to their product. Rule ({\sc{E-Read}})
evaluates an array read operation. It first evaluates $x$ to an array
value $[\overline{c_{i}}]_{n_{1}}$, and $e$ to a \kw{uint} value
$n$. It then returns $c_{n}$, the $n$-th index value in the array,
provided $n < n_{1}$, the length of the array. Rule ({\sc{E-Inp}})
evaluates to some constant $c$ denoting party $j$'s input. We model
the inputs to be base constants, an array input can be written in the
language as $[\kw{in}_{j}]_{n}$, which can then evaluate using the
rule ({\sc{E-Arr}}). The remaining rules are straightforward, and are
elided for space reasons.

@@

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Secret label} & m &::=& \mathcal{A} \mid \mathcal{B}\\
    \ftext{Label} & \ell &::=& \mathcal{P} \mid m\\
    \ftext{Type} & \tau &::=& \sigma^{\ell} \mid \sigma^{\ell}[n]\\
    \ftext{Expression} & \widetilde{e} &::=& c \mid x \mid \widetilde{e_{1}} \mulop_{\ell} \widetilde{e_{2}} \mid \widetilde{e_{1}} >_{\ell} \widetilde{e_{2}} \\
    & & \mid & \lcond{\ell}{{\widetilde{e}}}{{\widetilde{e_{1}}}}{{\widetilde{e_{2}}}} \mid x[\widetilde{e}] \mid [\overline{\widetilde{e_{i}}}]_{n} \mid \kw{in}^{m}_{j} \mid \widetilde{e} \rhd m\\
    \ftext{Statement} & \widetilde{s} &::=& \tau\:x = \widetilde{e} \mid x := \widetilde{e} \mid \dots \mid \widetilde{s_{1}}; \widetilde{s_{2}} \mid \dots\\
  \end{array}
  \]
\caption{Intermediate Language}
\label{fig:interlang}
\end{figure}

@@

Most of the expression forms $\widetilde{e}$ are same as $e$, except
that the binary operators, and the conditional forms
are annotated with label $\ell$, denoting how the operators should be
evaluated ($\mathcal{P}$ for in-clear, and $\mathcal{A}$ and
$\mathcal{B}$ for using arithmetic or boolean circuits resp.). The
form $\widetilde{e} \rhd m$ denotes coercing the value of $\widetilde{e}$ to be
$m$-secret shared. The statements $\widetilde{s}$ are analogous to
$s$.

\begin{figure}[t]
  \small
  \fbox{$\Gamma \vdash e : \tau \leadsto \widetilde{e}$}
  \[
  \begin{array}{c}
     \inferrule*[lab={\footnotesize{T-Cons}}]
               {
                 \tau = \mathsf{typeof}(c)^{\mathcal{P}}
               }
               {
                 \Gamma \vdash c : \tau \leadsto c 
               }

    %%  \inferrule*[lab={\footnotesize{T-Var}}]
    %%            {
    %%            }
    %%            {
    %%              \Gamma \vdash x : \Gamma(x) \leadsto x
    %%            }
\\\\

	  \inferrule*[lab={\footnotesize{T-Mult}}]
               {
                 \forall i \in \{1,2\}.\:\Gamma \vdash e_{i} : \kw{uint}^{\ell} \leadsto \widetilde{e_{i}}\\\\
                 \left(\ell = \mathcal{P}\right) \vee \left(\ell = \mathcal{A}\right)
               }
               {
                 \Gamma \vdash e_{1} \mulop e_{2} : \kw{uint}^{\ell} \leadsto \widetilde{e_{1}} \mulop_{\ell} \widetilde{e_{2}}
               }

     \inferrule*[lab={\footnotesize{T-Gt}}]
               {
                 \forall i \in \{1,2\}.\:\Gamma \vdash e_{i} : \kw{uint}^{\ell} \leadsto \widetilde{e_{i}}\\\\
                 \left(\ell = \mathcal{P}\right) \vee \left(\ell = \mathcal{B}\right)
               }
               {
                 \Gamma \vdash e_{1} > e_{2} : \kw{bool}^{\ell} \leadsto \widetilde{e_{1}} >_{\ell} \widetilde{e_{2}}
               }

     \inferrule*[lab={\footnotesize{T-Cond}}]
               {
                 \Gamma \vdash e : \kw{bool}^{\ell} \leadsto \widetilde{e}\\\\
                 \forall i \in \{1,2\}.\:\Gamma \vdash e_{i} : \sigma^{\ell'} \leadsto \widetilde{e_{i}}\\\\
                 \ell = \mathcal{P} \vee (\ell = \mathcal{B} \wedge \ell' =\mathcal{B})
               }
               {
                 \Gamma \vdash \cond{e}{e_{1}}{e_{2}} : \sigma^{\ell'} \leadsto \lcond{\ell}{\widetilde{e}}{\widetilde{e_{1}}}{\widetilde{e_{2}}}
               }

     \inferrule*[lab={\footnotesize{T-Arr}}]
               {
                 \forall i \in [n].\:\Gamma \vdash e_{i} : \sigma^{\ell} \leadsto \widetilde{e_{i}}
               }
               {
                 \Gamma \vdash [\overline{e_{i}}]_{n} : \sigma^{\ell}[n] \leadsto [\overline{\widetilde{e_{i}}}]_{n}
               }

  \end{array}
  \]
  \\\\
    \fbox{$\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$}
  \[
  \\
  \begin{array}{c}
     \inferrule*[lab={\footnotesize{T-Decl}}]
               {
                 \tau = \psi^\ell \\\\
                 \Gamma \vdash e : \tau \leadsto \widetilde{e}
               }
               {
                 \Gamma \vdash \psi\:x = e \leadsto \tau\:x = \widetilde{e} \mid \Gamma, x:\tau
               }

\subsubsection*{Source to Intermediate Compilation judgments} We provide the compilation
rules in \figureref{compile}. \divya{PL jargon?} We present the rules in a
declarative style, where the rules are non-syntax
directed, and the labels $\ell$ are chosen
non-deterministically. \sectionref{impl} describes the label  inference
scheme in our implementation.

Judgment $\Gamma \vdash e : \tau \leadsto \widetilde{e}$, where
$\Gamma$ maps variables $x$ to types $\tau$, says that
under $\Gamma$, $e$ (in source language) compiles to $\widetilde{e}$ (in intermediate language) with type $\tau$.

The rule ({\sc{T-Cons}}) assigns the label $\mathcal{P}$ to the
constants, as the constants are always public. Rule ({\sc{T-Mult}})
compiles a multiplication to either a public multiplication  ($\mulop_{\mathcal{P}}$), or a
secret arithmetic multiplication ($\mulop_{\mathcal{A}}$). As
our compiler is cryptographic cost aware, it never compiles the
multiplication to boolean multiplication $\mulop_{\mathcal{B}}$. In a similar manner,
rule ({\sc{T-Gt}}) compiles $e_{1} > e_{2}$ to either public comparison,
or secret boolean comparison. The rule for conditional
({\sc{T-Cond}}) has two cases: when the conditional expression $e$ is of
type $\kw{bool}^{\mathcal{P}}$, both the branches have a base type
$\sigma^{\ell'}$, for an arbitrary $\ell'$, and the conditional is
compiled to a public conditional, whereas when the conditional
expression has type $\kw{bool}^{\mathcal{B}}$, $\ell'$ is also
$\mathcal{B}$, and the conditional is compiled to a secret conditional
using a boolean circuit. Note that we restrict the type of the branches
to be of base type. 
Rule ({\sc{T-Read}}) type checks an array read. It checks
that the array index $e$ is public, and uses a static bounds checking
judgment $\Gamma \models e < n$ to prove that the array index is in
bounds. Section~\ref{sec:impl} discusses our implementation of bounds
checking. Rule ({\sc{T-Inp}}) picks a label $m$ for the input. Finally,
rule ({\sc{T-Sub}}) is the subsumption rule that coerces an expression of
type $\sigma^{\ell}$ to an expression of type $\sigma^{m}$ using the
coerce expression. It is important for security that the secrets cannot be coerced to public
values.

Judgment $\Gamma \vdash s : \tau \leadsto \widetilde{s} \mid \Gamma_{1}$
compiles a statement $s$ resulting in the statement $\widetilde{s}$
and type environment $\Gamma_{1}$. Rule ({\sc{T-Decl}}) picks a label
$\ell$, and adds the binding for $x$ to the environment. If $\psi = \sigma$, $\psi^\ell = \sigma^\ell$, else if $\psi = \sigma[n]$, $\psi^\ell = \sigma^\ell[n]$. 
Rule ({\sc{T-Assign}}) looks up the type of $x$ in $\Gamma$ and compiles $e$ to $\tilde{e}$ of same type.
Note that in this rule we restrict the type of variable $x$ to be of base type.
Rule ({\sc{T-For}}) adds the loop counter $x$ to $\Gamma$ at type
$\kw{uint}^{\mathcal{P}}$, and delegates type checking to the
\kw{while} form. The rule ({\sc{T-Write}}), similar to ({\sc{T-Read}}),
checks that the index has type $\kw{uint}^{\mathcal{P}}$, and is in
bounds. Rule ({\sc{T-Out}})
types the expression $e$ at some secret label $m$. Rule ({\sc{T-If}})
checks that the conditional expression is public, and rule
({\sc{T-Seq}}) sequences the type environments. Finally, the typing
rule for the (internal) \kw{while} form ensures that $x$ is mapped in
$\Gamma$ at type $\kw{uint}^{\mathcal{P}}$, and that $x \notin
\mathsf{modifies}(s)$--this is necessary for ensuring the termination
of our semantics.

@@

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{add}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \bval \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Is environ misplaced? Can we merge base value and circuit gate?}}
\label{fig:circuits}
\end{figure}

@@
